Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-22 paper-2023-acsos-pulverization.tex
A clear statement in RW about difference
larger code with little decrease in char spacing

\lstdefinelanguage{pulv}[]{Kotlin}{
%  basicstyle=\small\ttfamily\lst@ifdisplaystyle\footnotesize\fi,
%	frame=single,
%	escapechar=\%,
%  keywordstyle=\color{blue},
  keywordstyle=[3]\bfseries{},
  keywords=[3]{pulverizedSystem,device,and,deployableOn,pulverizationRuntime,startsOn,onDevice,reconfigurationRules,reconfigures,movesTo},
%  emph={DeviceBehaviour,DeviceCommunication,DeviceSensors,DeviceActuators,HighLoad,LowBattery},
%  sensitive=true,
%  morecomment=[l]{//},
%  morecomment=[n]{/*}{*/},
%  commentstyle=\color{green!40!black},
%  morestring=[b]",
%  morestring=[b]',
%  morestring=[b]""",
%  stringstyle=\ttfamily\color{orange},
}
\lstset{language=pulv,
basewidth=0.555em % decreases spacing between chars
}

@@

A \emph{deployment plan} is a configured mapping of a software system onto a deployment domain.
%
Given a deployable software system
developed using the techniques of the previous subsection,
 what is needed now is a language to describe a deployment domain
 and the deployment mapping.
%
Languages have been proposed
 targeting specific deployment domains
 such as the smart grid (cf. \emph{dspec} in the \emph{RIAPS} platform~\cite{DBLP:conf/coins/GhoshTKKL22})
 or the cloud (cf. the \emph{CAMEL} multi-\ac{dsl}~\cite{DBLP:journals/jcloudc/AchilleosKRKDOS19}).
%
In this work,
 we are especially interested in deployments over large-scale cyber-physical systems and the edge-cloud continuum.

A related \ac{dsl} is 
\emph{MuScADeL}~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel}:
it allows expressing deployment properties of
applications on multi-scale deployment domains,
i.e., large and heterogeneous infrastructures considered under several viewpoints
(device, geography, network, administrative domains, etc.).
%
Component descriptions can include \emph{constraints}
(both basic software/hardware constraints and multi-scale criteria).
%
The specifications are used to generate \emph{probe} artefacts supporting data collection at the level of the deployment middleware.
%
However, the work in~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel} is preliminary and does not cover runtime adaptation.

>>>>

\lstdefinelanguage{pulv}[]{Kotlin}{
 basicstyle=\small\ttfamily\lst@ifdisplaystyle\footnotesize\fi,
%	frame=single,
%	escapechar=\%,
%  keywordstyle=\color{blue},
  keywordstyle=[3]\bfseries{},
  keywords=[3]{pulverizedSystem,device,and,deployableOn,pulverizationRuntime,startsOn,onDevice,reconfigurationRules,reconfigures,movesTo},
%  emph={DeviceBehaviour,DeviceCommunication,DeviceSensors,DeviceActuators,HighLoad,LowBattery},
%  sensitive=true,
%  morecomment=[l]{//},
%  morecomment=[n]{/*}{*/},
%  commentstyle=\color{green!40!black},
%  morestring=[b]",
%  morestring=[b]',
%  morestring=[b]""",
%  stringstyle=\ttfamily\color{orange},
}
\lstset{language=pulv,
basewidth=0.52em % decreases spacing between chars
}

@@

A \emph{deployment plan} is a configured mapping of a software system onto a deployment domain.
%
Given a deployable software system
developed using the techniques of the previous subsection,
 what is needed now is a language to describe a deployment domain
 and the deployment mapping.
%
Languages have been proposed
 targeting specific deployment domains
 such as the smart grid (cf. \emph{dspec} in the \emph{RIAPS} platform~\cite{DBLP:conf/coins/GhoshTKKL22})
 or the cloud (cf. the \emph{CAMEL} multi-\ac{dsl}~\cite{DBLP:journals/jcloudc/AchilleosKRKDOS19}).
%
In this work,
 we are especially interested in deployments over large-scale cyber-physical systems and the edge-cloud continuum.
%
The main aspects distinguishing \ourframework{} from other approaches are that it targets \emph{pulverised systems} (and not general partitionings) and that it uses internal \acp{dsl} embedded in Kotlin.

A related (external) \ac{dsl} is 
\emph{MuScADeL}~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel}:
it allows expressing deployment properties of
applications on multi-scale deployment domains,
i.e., large and heterogeneous infrastructures considered under several viewpoints
(device, geography, network, administrative domains, etc.).
%
Component descriptions can include \emph{constraints}
(both basic software/hardware constraints and multi-scale criteria).
%
The specifications are used to generate \emph{probe} artefacts supporting data collection at the level of the deployment middleware.
%
However, the work in~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel} is preliminary and does not cover runtime adaptation.
